\pkg{Rgbp}: An R Package for Hierarchical Modeling and Method Checking

### 2013-06-18 jss/article.tex
starting up

\begin{document}

%% include your article here, just as usual
%% Note that you should use the \pkg{}, \proglang{} and \code{} commands.

@@

A function ``\code{summary}'' shows selective information on hospitals and more detailed estimation result as below. To be specific, it displays some hospitals (not all as above) with minimum, median, and maximum caseloads ($n_{j}$). On top of that, more specific estimation results, such as the estimation result of $\alpha\equiv\log(1/r)$, follow. Note that when we do not know the prior mean in advance unlike this hospital problem, \code{gbp} fits a linear regression for the Normal model, a log-linear regression for the Poisson model, or a logistic regression for the Binomial model and a summary of regression fit will appear.
\begin{CodeChunk}
\begin{CodeInput}
R> summary(p)
\end{CodeInput}error:%20LaTeX%20Error:%20File%20`a4wide.sty'%20not%20found.
\begin{CodeOutput}
Main summary:

@@

Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated. Hence, we can use \code{gbp} to fit this hierarchical model:

@@

         obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
5           -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
2            8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
7           18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
4            7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
6            1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
1           28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
3           -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
colMeans     8.75 12.5      8.168     0.552   -9.163     8.168   25.723   8.900
\end{CodeOutput}
\end{CodeChunk}
The output from \code{gbp} provides an easy to read summary of the results of the estimation. Here we see that the posterior mean estimates are simply a linear combination

>>>>

\begin{document}
%% include your article here, just as usual
%% Note that you should use the \pkg{}, \proglang{} and \code{} commands.

@@

A function ``\code{summary}'' shows selective information on hospitals and more detailed estimation result as below. To be specific, it displays some hospitals (not all as above) with minimum, median, and maximum caseloads ($n_{j}$). On top of that, more specific estimation results, such as the estimation result of $\alpha\equiv\log(1/r)$, follow. Note that when we do not know the prior mean in advance unlike this hospital problem, \code{gbp} fits a linear regression for the Normal model, a log-linear regression for the Poisson model, or a logistic regression for the Binomial model and a summary of regression fit will appear.
\begin{CodeChunk}
\begin{CodeInput}
R> summary(p)
\end{CodeInput}
\begin{CodeOutput}
Main summary:

@@

Due to the nature of the test each school's coaching effect has an approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated. Hence, we can use \code{gbp} to fit a Normal-Normal hierarchical model:

@@

         obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
5           -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
2            8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
7           18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
4            7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
6            1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
1           28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
3           -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
colMeans     8.75 12.5      8.168     0.552   -9.163     8.168   25.723   8.900
\end{CodeOutput}
\end{CodeChunk}
The output from \code{gbp} provides an easy to read summary of the results of the estimation. There seems to be little evidence
